TBA

### 2019-10-07 paper.tex
Adding proper IP plot

Analysis of the elevation data with the Friedman test reveals that the results for the different settings within each group are indeed significantly different from one another with a reasonable degree of confidence ($p_{G1} = 0.03, p_{G2} = 0.01$).
A post-hoc analysis using the Wilcoxon signed rank test with a Holm-Bonferoni correction applied to the commonly used 0.05 statistical significance threshold was used to investigate the setting relationships more closely. 
This analysis reveals that there is only 1 significant difference between the performances generated by the \textit{med} and \textit{hi} settings for Group \textit{G1} ($p_{med-hi} = 0.002$}, while Group \textot{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/fitts_fit.png}
  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
\end{figure}

>>>>

Analysis of the elevation data with the Friedman test reveals that the results for the different settings within each group are indeed significantly different from one another with a reasonable degree of confidence ($p_{G1} = 0.03, p_{G2} = 0.01$).
A post-hoc analysis using the Wilcoxon signed rank test with a Holm-Bonferoni correction applied to the commonly used 0.05 statistical significance threshold was used to investigate the setting relationships more closely. 
This analysis reveals that there is only 1 significant difference between the performances generated by the \textit{med} and \textit{hi} settings for Group \textit{G1} ($p_{med-hi} = 0.002$), while Group \textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
With these results, we can reasonably conclude that the \textit{hi} setting  
The distributions in \cref{fig:target-boxplot-error} show that the \textit{hi} setting produces the smallest median angular error in the elevation dimension out of the 3 settings and the post-hoc tests performed allow us to make the conclusion that the \textit{hi} setting is indeed the best setting to produce the lowest error.

\subsection{Time to Target}

To investigate if the interface has a Fitts-relationship, we plot the time to find the target as a function of the targets' indices of difficulty as defined in \cref{eq:fitts-base}.
The data was binned in intervals of the effective target width as given by \cref{eq:fitts-we} and are plotted for each gradient setting. 
A logarithmic line of best fit is fitted through the binned data's median values through means of regression and all the results are presented in \cref{fig:fitts-results}.

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/fitts_fit.png}
  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
  \label{fig:fitts-results}
\end{figure}

For Group \textit{G1}, a Fitts relationship can be observed where the logarithmic line of best fit closely approximates the median values of the binned data for all 3 settings. 
This is confirmed with strong Pearson correlation scores for each setting ($r_{lo} = 0.9, p_{lo} = 0.03; r_{med} = 0.92, p_{med}=0.009; r_{hi} = 0.86, p_{hi} = 0.02$).
This result allows us to calculate and plot the index of performance, as given in \cref{eq:fitts-ip}, for each setting in \cref{fig:fitts-ips}.

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/fitts_ips.png}
  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
  \label{fig:fitts-ips}
\end{figure}
